\blue{...Numerical investigation of viscous flow instabilities through heterogeneous porous media using adaptive and unstructured meshes under different mobility scenarios...}

### 2017-07-11 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

In Section~\ref{section:results_homo_hete}, the impact of viscosity ratio on the nucleation of fingers was demonstrated in homogeneous porous media

>>>>

In Section~\ref{section:results_homo_hete}, the impact of viscosity ratio on the growth of fingers and the triggering effect of heterogeneity on instability nucleation were demonstrated in modified simulated Hele-Shaw cells.
